% YAAC Another Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/yaac-another-awesome-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%Section: Work Experience at the top
\sectionTitle{Professional Experience}{\faSuitcase}
%\renewcommand{\labelitemi}{$\bullet$}
\begin{experiences}
\emptySeparator
\experience
    {Till Now}     {Senior Software Engineer}{FreightExchange}{Remote}
    {June 2022}    {
                      \begin{itemize}
                        \item Handle end to end process- Design, code and deployment of freight management system (\url{https://app.freightexchange.com.au/})
                        \item Created the framework to make carrier integration easy and configurable.
                        \item Design, Develop and scale Quote and Booking algorithm.
                      \end{itemize}
                    }
                    {Java, Spring, Mysql, SpringBoot, Redis, SQS, AWS}
\experience
    {May 2022}     {Lead Software Engineer}{Sinch(ACL Mobile)}{Noida}
    {February 2020}    {
                      \begin{itemize}
                        \item Design and Developed Workflow Engine(Customer Journey Orchestration Engine).
                      \end{itemize}
                    }
                    {Java, NodeJs, Mysql, SpringBoot, Redis, SpringBatch}
\emptySeparator

\experience
    {September 2019} {Senior Software Engineer}{DoubleYou Technology}{Gurugram}
    {August 2015}    {
                      \begin{itemize}
                        \item Designed and Developed various micro-services - Recommendation, Notification service, Profile review portal
                        \item Developed Recommendation algorithm which generates recommendations according to user’s gender, location, age, popularity using Mysql and Redis(caching)                      
                        \item Developed Notification System using AWS SQS.
                                                
                        \item Developed user popularity score service.
                        
                        \item Developed Notification scheduling system using AWS SQS delayed message functionality.                         
                      \end{itemize}
                    }
                    {Java 1.8, Git, Hibernate, Spring, AWS Kinesis, Redis, AWS SQS, DynamoDb, Tomcat 1.8, Maven}

  \emptySeparator
  \experience
    {August 2015} {Software Engineer}{Infotrellis Inc.}{Chennai}
    {July 2013}    {
                      \begin{itemize}
                        \item Helped develop data pipeline for Allsight. Data is collected from various social media sources and converted to Allsight 360 model. This module is developed using Kafka and Storm.              
                        \item Worked on matching engine which finds a match between customer data and social media data. It uses full text search on collected data using elasticserarch and JanusGraph backed by Hbase to create identity graph. 
                      \end{itemize}
                    }
                    {Hadoop, Pig , HBase, ElasticSearch, JanusGraph, Storm, Kafka}
\end{experiences}
